At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.

### 2019-11-27 manuscript/reply_to_referees_2.tex

\begin{document}

\begin{letter}{\bf Dr. Jana Vamosi\\
               Editor\\
               Proceedings of the Royal Society B\\
               6-9 Carlton House Terrace\\
               London, UK\\
               SW1Y 5AG\\
                }

\opening{Dear Dr. Vamosi:}

We are pleased to submit a revised version of our manuscript, NPH-MS-2019-30803. In response to a suggestion from Referee 3, we have retitled it "". We have also taken care to revise our methods section in response to the many helpful suggestions from Referee 4, and hope that our approach is now clearer. Finally, we have expanded the discussion to include some additional concepts suggested by Referees 2 and 4, and a possible application of our research suggested by Referee 3.

Given the difference of opinion between Referees 1, 3, and 4 and Referee 2, we have prioritised adjusting the manuscript according to the majority view. We must also admit to having some difficulty parsing a number of Referee 2's comments in order to find what is being asked/suggestions. Nevertheless, we appreciate their time and effort in offering such extensive feedback. We have taken care to address each of Referee 2's comments and, where possible, have used them to improve the manuscript.

We appreciate all of the Referee's comments and are confident that our manuscript is all the stronger for responding to them.

@@

\end{letter}

\newpage

\setcounter{page}{1}

% NPH-MS-2019-30803 At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.
% by Cirtwill, Alyssa; Dalla Riva, Giulio; Baker, Nick; Ohlsson, Mikael; Norström, Isabelle; Wohlfarth, Inger-Marie; Thia, Josh; Stouffer, Daniel

% Dear Dr Cirtwill

% I write you in regard to your submitted manuscript, NPH-MS-2019-30803 "At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”, which has now been reviewed. We found four reviewers (some original reviewers and some new) and they all generally enjoyed your revised manuscript. However, they also provided suggestions for some expanding certain sections and providing additional clarification. In particular, Reviewer \#2 and \#4 provide some detailed suggestions, especially with regard to keeping the aims and logic consistent, that will help strengthen the manuscript.

% Although resolving these issues will require some restructuring, I think you should be able to handle these suggestions through revision (see below) and, ultimately, this manuscript will make a nice contribution to the literature.

% Please carefully revise your manuscript and resubmit your revised version within 4 weeks. Please also include a summary of how you have incorporated the suggestions of the reviewers.

% Thank you for submitting your work to New Phytologist.

% Sincerely,

% Jana Vamosi

% Editor, New Phytologist

% Decision: Accept subject to revision

@@

	22. Typo in Fig. 1 caption [[done]]

		\begin{refquote}
			Fig 1. "...the probability of a pair of plants sharing an interaction partner increased with increasing phylogenetic distance..." please, write decreased instead of increased.
		\end{refquote}

		\textbf{R:} We thank the Referee for pointing out this truly egregious typo, and have corrected it.

	23. Difference between minimum and maximum slopes not visible [[done]]

@@

		\begin{refquote}
			Fig 2. It is no clear for us. Minimum and maximum slopes obtained from 999 permutations are the same value?
		\end{refquote}

		\textbf{R:} As the caption states, the minimum and maximum slopes were always very close to 0. We therefore had to choose between a y-axis scale which would show the observed slopes or one which would show the differences in slopes for the permutations. As the  observed slopes are far more important than knowing the exact values of the permutation slopes, we chose to prioritise the former.

@@

			\smallskip

			Figure 3 is only referenced in the text when talking about herbivory networks but not for pollination networks.
		\end{refquote}

		\textbf{R:} We have reordered the tables and added a redundant reference to Fig. 3.

	26. Suggestion to include ideas about evolution and coevolution [[done]]

@@

		\begin{refquote}
			Discussion
			General
			We suggest you include ideas about evolution and coevolution in networks in your discussion. It is important to recognize that network structure is in part a consequence of the evolutionary process and that we cannot think in the pairwise-coevolutionary framework as the only one modulating trait evolution in species rich assemblages.
			You state that the fact that the proportion of specialist species may explain differences between plant-pollination and plant-herbivore network patterns and you discuss the mathematical consequences of such difference but you should discuss the ecological and evolutionary causes and consequences of having higher specialization in pollination networks. This is also related with your methodological decision of excluding more specialized herbivores, isn't it?
		\end{refquote}

		\textbf{R:} We do include ideas about evolution and coevolution inour discussion. We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks. However, since we do not have trait or genetic data for our networks, we cannot comment with any certainty on which of our results are due to trait plasticity or environmental influence and which are due to evolution. We therefore mention possible evolutionary and ecological explanations together.

		Specialists, for example, could have co-evolved with particular interaction partners. They could also, however, be able to interact with more species which simply do not appear in the study site due to competition, unsuitable soil conditions, etc. As Referee 4 notes, specialists may also simply be species which were sampled more rarely. That is, we may be missing interactions involving these species which actually do occur. Please note that the proportion of specialists is a potential explanation for the results we observed and not a key result in itself. As such, we feel that spending a great deal of time trying to explain this trend would distract readers from the main message of our paper.

		Some examples of evolutionary ideas in the discussion:

			This relationship between overlap and 
			phylogenetic distance is consistent with the idea that traits affecting 
			interactions are heritable and change gradually
			such that closely related plants resemble their common ancestor--- and
			  each other ---more than they do distantly related 
			  plants~\citep{Schemske1999,Gilbert2015,Ponisio2017}. The degree of 
			  heritability of key traits may, however, differ between families. In
			  some families, such as \emph{Asteraceae} in pollination networks, 
			  the positive slope of this relationship was very shallow while in 
			  others, such as \emph{Melastomataceae} in herbivory networks, the 
			  positive slope was extremely steep. This could indicate different 
			  rates of phenotypic drift or evolution in different families. 
			  In other families, there was no significant relationship between phylogenetic
			  distance and interaction partner overlap. In these cases, key traits affecting 
			  plant-insect interactions may not be strongly
			  conserved. Studies showing a stronger relationship between trait similarity
			  and shared interaction partners than phylogenetic similarity and shared
			  interaction partners suggest that traits may indeed be evolutionarily
			  labile~\citep{Junker2015,Ibanez2016,Endara2017}.

			In other plant families
			  with more moderate levels of specialisation, it is possible 
			  that pollination and/or herbivory do not exert large
			  selection pressures on the plants. If traits affecting pollination
			  or herbivory are not heritable in these groups [\citealp{Kursar2009}] 
			  or their phenotypes are constrained by other factors (e.g., 
			  environmental conditions, trade-offs with other traits, ontogenic
			  change [\citealp{Karinho2014}]), then we should not expect a relationship 
			  between phylogenetic distance and overlap of interaction partners.

		See also lines XX-XX, where we discuss constraints on traits. We have lightly revised these lines to reference evolution explicitly.

		 This may indicate that one type of interaction
		  places greater evolutionary constraints upon these families than the other, 
		  similar to the expectation that greater constraints upon consumers 
		  than upon their resources explains the asymmetry in conservation  
		  of interaction partners~\citep{Fontaine2015}. Plants
		  may not be able to respond to selection on both types of interaction
		  simultaneously because traits affecting pollination can also affect herbivory, and vice
		  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
  		\end{quotation}

	27. Objection to the word "broad" [[done]]

		\begin{refquote}
			338-339. You state We found broad support for the hypothesis that more closely-related pairs of plants have a higher degree of niche overlap. This is a very strong sentence that is not supported by your results. You found evidence in 55\% of plant-pollination networks (almost half of your dataset). In fact, it is interesting to note that even the slope is more pronounced in mutualistic networks you found higher support in herbivory networks, as a higher percentage of networks showed a tendency.
		\end{refquote}

		\textbf{R:} Note that 56\% is greater than half, and that when all networks were considered together we also observed the same trends. We contend that these two facts do represent broad support for our hypothesis. It is not, of course, universal support. That is why we A) did not claim universal support and B) provide the numbers of networks. Readers are thereby armed with the tools to agree or disagree with our choice of words. In case it is the synonymy between broad and general that has perplexed the Referee, we have changed this line to state ''We found \emph{general} support...''. We hope that this is clearer.

		With the unbalanced sample sizes of pollination and herbivory networks, we are somewhat reluctant to make much of the difference between 56\% of pollination networks and 64\$ of herbivory networks. We consider that the important point here is that networks are more likely than not to show decreasing niche overlap with increasing phylogenetic distance.

@@

		\textbf{R:} Note that 56\% is greater than half, and that when all networks were considered together we also observed the same trends. We contend that these two facts do represent broad support for our hypothesis. It is not, of course, universal support. That is why we A) did not claim universal support and B) provide the numbers of networks. Readers are thereby armed with the tools to agree or disagree with our choice of words. In case it is the synonymy between broad and general that has perplexed the Referee, we have changed this line to state ''We found \emph{general} support...''. We hope that this is clearer.

		With the unbalanced sample sizes of pollination and herbivory networks, we are somewhat reluctant to make much of the difference between 56\% of pollination networks and 64\$ of herbivory networks. We consider that the important point here is that networks are more likely than not to show decreasing niche overlap with increasing phylogenetic distance.

	28. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common [[done]]

		\begin{refquote}
			351-352 The herbivory networks did not contain as many obligate specialists, but we note that many herbivorous insects are oligotrophs which consume only a few closely-related hosts (Novotny \& Basset, 2005; Yguel et al., 2011). This sentence is confuse because you have a subsample of herbivory networks and then this seems to be a by-product of your study design associated with your decision of removing networks that may show strong phylogenetic signal.
		\end{refquote}

		\textbf{R:} We must again point out that subsetting the herbivory networks as we have done was requested during an earlier round of review. We are therefore reluctant to reconsider this approach without a very good reason.

		Beyond that, it is very difficult to work out exactly what the Referee objects to in this sentence. If the Referee is objecting to our references, note that~\citet{Novotny2005} addresses leaf-chewers as intermediate in their level of specialisation on particular families and emphasises that herbivores in general (regardless of guild) tend to consume a few closely-related hosts. They point out the relative rarity of strict specialists compared to specialists on species within a particular genus or family.~\citet{Brandle2006} also found insect herbivores were specialised on a particular genus but consumed multiple species within the genus. As~\citet{Brandle2006} focus on phytophagous insects specifically, we feel that this reference addresses our point more directly than~\citet{Yguel2011}. We have therefore replaced this reference. We hope that this improved selection of references will help the Referee's confusion.

@@

		If the Referee objects to our finding that the herbivores in our networks tended to consume more than one plant species, there is little we can do about it. That is simply what our data say. We do not feel that it is appropriate to look for explanations in the trends we observe in our networks in other types of networks.

		If the Referee is contending that, because of the multiple herbivore types in~\citet{Novotny2005}, we cannot claim that the herbivores in our dataset are oligotrophs, we can respond with further details. The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36, and the median ranged bewteen 1 and 11.5 (mean 4.68). These measures indicate that many herbivores in our networks do, in fact, consume only a few of the plants available to them. Our point therefore stands.

	29. Claims that congeneric species are not closely related [[No convincing reason to change]]

@@

		\begin{refquote}
			357-359 This suggests that conservation of interaction partners among closely related plants (e.g., congeners or members of the same subfamilies) is more important than phylogenetic signal from deeper within the phylogenetic tree. Congeneric species can be not closely related, please revise sentences like this one across the manuscript because you are confounding phylogeny with taxonomy.
		\end{refquote}

		\textbf{R:} Does the Referee really mean to suggest that plants in the same genus are less closely-related than plants in different families? Without some sources to substantiate this, we find this claim very far-fetched! This is especially surprising given the Referee's insistence that we should expect similar interaction partners within a family. We agree that taxonomy is only a proxy for phylogeny, but we are not aware of any evidence that it is a poor proxy. We note that across seven other reviews, no other Referee has commented on this. Based on this lackof objection and similar language throughout the literature, we have opted not to change this line.

	30. Another demand to discuss intimacy [[done. Look for more places to scattershot Hembry]]

@@

		\begin{refquote}
			361-365. How interaction intimacy may explain your results? Please, discuss your results in light of the interplay between interaction type (pollination, herbivory) and intimacy (see Hembry et al. 2018).
		\end{refquote}

		\textbf{R:} We do not have any data on interaction intimacy, nor did we test for reciprocal specialisation, so we cannot say how this would influence our results. At a guess, we would guess that leaf-chewing herbivory and pollination are both low-herbivory interactions. We would therefore naively expect similar trends. We note that~\citet{Hembry2018} only study a very small and high-intimacy system (a single genus of brood pollinating moths and their single genus of host plants). Their results will therefore not necessarily generlize to the larger, more diverse networks we consider. Indeed, had they considered a broader sample of plants and seed predators or herbivores from the same islands, they easily could have found less reciprocal specialisation. As a detailed study of this unusual mutualism was the aim in~\citet{Hembry2018} this is not a problem for their work, but we are hesitant to infer too strong a relationship between their findings and ours.

		This reference suggestion is also somewhat confusing as~\citet{Hembry2018} did not find evidence for host-associated differentiation in their moths. This would seem to undermine the Referee's fervent belief that evolution/coevolution can explain network structure. Moreover, they point out that the support for the intimacy hypothesis  in their system was broad (in the same sense we used the word) but equivocal. This exacerbates the difficulty of extrapolating their work to explain our results.

		Given all of the above, it is hard to see how the interaction intimacy hypothesis relates to these lines (which are about whether the number of species in dfferent plant families is related to the strength of phylogenetic signal). Instead, we feel that a discussion of the possible effects of intimacy is more relevant later on, where we discuss possible reasons why some families may show different trends. Although we cannot test this, some families may interact more intimately with their pollinators/herbivores. This could result in more specialised relationships and weaker signal. We had mentioned this possibility briefly in lines 406-407 of the previous version, but are happy to expand upon this point somewhat. This section (lines XX-XX) now reads:

			Indeed, animal pollination and seed dispersal have been shown to act
		  	as filters for several plant clades~\citep{Mayfield2009}, while selection to avoid 
		  competition and restriction on numbers of interaction partners may lead to
		  more intimate or specialised interactions~\citep{Ponisio2017}. 
		  Reciprocal specialisation is particularly expected to occur in highly intimate interactions~\citep{Hembry2018}. Although pollination and leaf-chewing herbivory are both relatively low-intimacy interactions, it is still possible that some plant families may tend to have more intimate interactions than others. This could result, for example, if a plant is pollinated by an insect which is also a herbivore in its larval stage~\citep{Hembry2018}. Testing this possibility is beyond the scope of the present manuscript, but could be interestting for future work.

@@

\clearpage

{\Large \bf Reply to Referee 3} [[Still to do: title, add a bit about how this could be relevant for conservation.]]

	\begin{refquote}
		The study is well designed and the manuscript well written, and the authors clearly demonstrate their comprehensive grasp of the subject and the applied statistical analyses.
		My only more general comment is whether authors have considered potential applications of such phylogenetic approaches for ecological restoration? If closely-related species provide similar functions in ecological networks, they could be used interchangeably to restore ecological interactions/functions. This is an exciting potential application of phylogenetic data in biodiversity conservation and restoration, and could be touched upon/discussed in this manuscript.. 
		Otherwise, I have only minor comments.
	\end{refquote}

	\textbf{R:} We thank the Referee for their compliments to our approach and to our writing, as well as their more detailed comments (addressed one-by one below; replies preceded by \textbf{R:}). We had not considered this potential application for ecological restoration but are very pleased to have it pointed out. It is often difficult to see how theoretical work may relate to conservation practice, so we are glad to take the opportunity to make a link here. [[Add a bit of this, I think we have room]] [[May make a good closing line?!?]]

@@

		\begin{refquote}
			Title is confusing – difficult to pick out key message. And given that your analyses broadly give support for effects of phylogenetic distance on niche overlap, why not focus on this message, rather than variability at among individual networks/plant families
		\end{refquote}

		\textbf{R:}

"At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”

- suggests that we focus on broad support. Maybe "Broad conservation of pollinators and herbivores in a global dataset"?
"Despite variation among families, pollinators and herbivores are broadly conserved among related plants"?
"Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families"?

@@

\clearpage

{\Large \bf Reply to Referee 4} [[done]]

	\begin{refquote}
		Understanding what drives the structure of networks of interactions is key to predict the structure of plant-insect communities (e.g., for conservation or restoration purposes, or to support benefit organisms in agriculture).
		The present study focuses on the contribution of the evolutionary history to the interaction structure, and makes a significant contribution to the understanding of the variability of the phylogenetic signal in plant-insect networks. Here, the strength of the phylogenetic signal is actually quantified while it usually relies on correlation scores, and the effect of plant composition and the identity of plant families are examined to assess whether they could explain the variability of trends described in the literature.
		The dense writing turns out to be a double-edge sword: a lot of information on drivers of phylogenetic signals is compiled in here, but the text is sometime hard to follow. Hence, my following comments mostly pertains to the form, and I trust the authors should be able to address them fairly easily.
	\end{refquote}

	\textbf{R:} We thank the Referee for their compliments to our analysis and for taking the time to review our manuscript. We appreciate that our writing can be dense at times and appreciate the Referee pointing out places where we may clarify our prose. We especially appreciate the detailed suggestions for how to improve our second-to-last paragraph, and have followed them to the best of our ability. Below, we respond to each comment in detail (preceded by \textbf{R:}). We are confident that revising the manuscript in response to the Referee's comments has improved the manuscript.

@@

	1. Confusion about description of two dependent variables in analyses [[done]]

### 2019-11-27 manuscript/phylogenetic_signal_manuscript.tex
think I've finished R2

    Models for two families did not converge. In the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} (represented by five species in one herbivory network and five species in two pollination networks), only one pair of species per network type shared any interaction partners while all other pairs did not share any interaction partners.

@@

  We found broad support for the hypothesis that more
  closely-related pairs of plants have a higher degree
  of niche overlap. Using a novel method which considers
  all pairs of plants together, 
  the probability of two plants sharing the same animal 
  interaction partners generally decreased with increasing 
  phylogenetic distance. Considering networks separately,
  $\approx$56\%  of the pollination and $\approx$64\% of the 
  herbivory networks exhibited the expected trend of decreasing 
  overlap with increasing distance. This variation between networks
  echoes earlier studies \citep[e.g.,][]{Fontaine2015,Hutchinson2017},
  which also found broad evidence for phylogenetic conservation 
  of interaction partners despite variation between particular 
  networks. The lack of a significant relationship between
  phylogenetic distance and interaction partner overlap in many
  networks could be partly due to the large number of extreme
  specialists, especially among the pollination networks.
  These species interact with only one plant and
  therefore weaken any signal of interaction partner overlap.
  The herbivory networks did not contain as many obligate 
  specialists, but we note that many herbivorous insects are
  oligotrophs which consume only a few closely-related 
  hosts~\citep{Novotny2005,Brandle2006}.
  These oligotrophs may affect overall phylogenetic signal in the same
  way as the specialist partners: in both cases plants in different
  families are unlikely to share interaction partners.

@@

  Moreover, \emph{Polygonaceae} in pollination networks and 
  \emph{Fabaceae} in herbivory networks showed the opposite 
  pattern to what we expected. In these families, closely-related plants had 
  \emph{lower} overlap than more distantly-related pairs of plants. 
  There are several possible reasons a plant family might
  display this pattern. First, part of the family may have recently 
  undergone a period of rapid diversification with closely-related species 
  developing novel phenotypes that attract different animal 
  interaction partners~\citep{Linder2008,Breitkopf2015}. It is also possible that the
  animals have undergone an adaptive radiation to 
  specialise on their most profitable partner~\citep{Janz2006}. Second, this pattern 
  could be the result of ecological or environmental 
  filtering~\citep{Ackerly2003,Mayfield2009}. 
  Closely-related species which have high degrees of overlap in their interaction 
  partners might compete too severely to coexist. This is especially likely
  for plants sharing pollinators, where the loss of pollen to related species 
  might severely limit reproductive success~\citep{Levin1970,Bell2005,Mitchell2009}.
  Indeed, animal pollination and seed dispersal have been shown to act
  as filters for several plant clades~\citep{Mayfield2009}, while selection to avoid 
  competition and restriction on numbers of interaction partners may lead to
  more intimate or specialised interactions~\citep{Ponisio2017}. This is
  consistent with the relatively high proportion of extreme specialists we
  observed in the pollination networks, which likely contributes to the weak
  relationships between phylogenetic distance and interaction partner overlap
  in many networks. Finally, although we do not have information about plants'
  traits in these networks, it is possible that convergence or a high degree of
  ancestral trait conservation has occurred
  allowing distantly-related \emph{Polygonaceae} and \emph{Fabaceae} to
  interact with the same insects.

@@

  For those few families which were well-represented in \emph{both} pollination
  and herbivory networks, we can also contrast the 
  trends in the two network types. While \emph{Asteraceae} showed the
  expected decrease in interaction partner overlap with increasing
  phylogenetic distance, the other families showed different trends in
  different network types. This may indicate that one type of interaction
  places greater constraints upon these families than the other, 
  similar to the expectation that greater constraints upon consumers 
  than upon their resources explains the asymmetry in conservation  
  of interaction partners~\citep{Fontaine2015}. Plants
  may not be able to respond to selection on both types of interaction
  simultaneously because traits affecting pollination can also affect herbivory, and vice
  versa~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
  Associations with pollinators and herbivores may also be constrained by the
  larger structure of the community. In one recent study, plants which are 
  visited by many pollinators are also consumed by many herbivores~\citep{Sauve2016}.
  This may be because pairing antagonistic and mutualistic interactions
  balances the indirect effects of these interactions, leading to a
  more stable community~\citep{Sauve2014}. As more networks describing 
  pollination and herbivory in the same community become available, it 
  will be interesting to test this hypothesis more thoroughly.

@@

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[height=.75\textwidth]{Figures/dataplots/observed_vs_random.eps}}
    \end{center}
     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance (representing the change in log odds of a pair of plants sharing an interaction partner) was signficantly different from 0 for each network. Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks. Thick, dashed lines represent the mean slopes across all networks of each type. The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines. For both network types, the slopes obtained from permuted networks were always very close to 0.}
    \label{obs_vs_random} 
  \end{figure}

>>>>

    Models for two families did not converge. In the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} (represented by five species in one herbivory network and five species in two pollination networks), only one pair of species per network type shared any interaction partners while all other pairs did not share any interaction partners. By considering each family separately, we do risk obtaining some significant results purely by chance. The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}. To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezler2016} (\emph{Supplemental Information 4}).

@@

  We found general support for the hypothesis that more
  closely-related pairs of plants have a higher degree
  of niche overlap. Using a novel method which considers
  all pairs of plants together, 
  the probability of two plants sharing the same animal 
  interaction partners generally decreased with increasing 
  phylogenetic distance. Considering networks separately,
  $\approx$56\%  of the pollination and $\approx$64\% of the 
  herbivory networks exhibited the expected trend of decreasing 
  overlap with increasing distance. This variation between networks
  echoes earlier studies \citep[e.g.,][]{Fontaine2015,Hutchinson2017},
  which also found broad evidence for phylogenetic conservation 
  of interaction partners despite variation between particular 
  networks. The lack of a significant relationship between
  phylogenetic distance and interaction partner overlap in many
  networks could be partly due to the large number of extreme
  specialists, especially among the pollination networks.
  These species interact with only one plant and
  therefore weaken any signal of interaction partner overlap.
  The herbivory networks did not contain as many obligate 
  specialists, but we note that herbivores, as well as pollinators, often interact with only a few closely-related plants~\citep{Novotny2005,Brandle2006,Astegiano2017}.
  These oligotrophs may affect overall phylogenetic signal in the same
  way as the strict specialists: in both cases plants in different
  families are unlikely to share interaction partners since the interaction partners tend to only visit plants within a particular genus. It is also likely that at least some of the apparent specialists in our dataset are actually rare species for which many interactions have not yet been observed~\citep{Bluthgen2006,Poisot2015}. Without information on the sampling completeness of the networks in our dataset, it is difficult to estimate the size of this effect. In any case, the degree of phylogenetic conservation of interaction partners may change as we obtain more complete data on rare species.

@@

  [[I don't like this paragraph. Refine?]]
  Moreover, \emph{Polygonaceae} in pollination networks and 
  \emph{Fabaceae} in herbivory networks showed the opposite 
  pattern to what we expected. In these families, closely-related plants had 
  \emph{lower} overlap than more distantly-related pairs of plants. 
  There are several possible reasons a plant family might
  display this pattern. First, part of the family may have recently 
  undergone a period of rapid diversification with closely-related species 
  developing novel phenotypes that attract different animal 
  interaction partners~\citep{Linder2008,Breitkopf2015}. It is also possible that the
  animals have undergone an adaptive radiation to 
  specialise on their most profitable partner~\citep{Janz2006}. Second, this pattern 
  could be the result of ecological or environmental 
  filtering~\citep{Ackerly2003,Mayfield2009}. 
  Closely-related species which have high degrees of overlap in their interaction 
  partners might compete too severely to coexist. This is especially likely
  for plants sharing pollinators, where the loss of pollen to related species 
  might severely limit reproductive success~\citep{Levin1970,Bell2005,Mitchell2009}.
  Indeed, animal pollination and seed dispersal have been shown to act
  as filters for several plant clades~\citep{Mayfield2009}, while selection to avoid 
  competition and restriction on numbers of interaction partners may lead to
  more intimate or specialised interactions~\citep{Ponisio2017}. 
  Reciprocal specialisation is particularly expected to occur in highly intimate interactions~\citep{Hembry2018}. Although pollination and leaf-chewing herbivory are both relatively low-intimacy interactions~\citep{Astegiano2017}, it is still possible that some plant families may tend to have more intimate interactions than others. This could result, for example, if a plant is pollinated by an insect which is also a herbivore in its larval stage~\citep{Hembry2018}. Testing this possibility is beyond the scope of the present manuscript, but could be interestting for future work. 
  Past selection to avoid competition is 
  consistent with the relatively high proportion of extreme specialists we
  observed in the pollination networks, which likely contributes to the weak
  relationships between phylogenetic distance and interaction partner overlap
  in many networks. Finally, although we do not have information about plants'
  traits in these networks, it is possible that convergence or a high degree of
  ancestral trait conservation has occurred
  allowing distantly-related \emph{Polygonaceae} and \emph{Fabaceae} to
  interact with the same insects.

@@

    For those few families which were well-represented in \emph{both} pollination
  and herbivory networks, we can also contrast the 
  trends in the two network types. Notably, all families except \emph{Asteraceae} 
  showed different trends in different network types. 
  This could be because of conflicting selection from pollinators and herbivores,
  with one type of selection placing greater constraints on plant traits than the other.
  Multiple types of interactions (e.g., pollination, herbivory, nectar robbing) 
  and even environmental factors can influence traits such as 
  flower colour, nectar abundance, and flowering phenology~citep{Strauss2006}. 
  These influences can act in the same or different directions~\citep{Strauss2006}.
  Plant phenotypes in turn affect which species participate in both pollination and herbivory~\citep{Strauss1997,Strauss2002,Adler2004,Adler2006,Theis2006}.
  The interplay between these different selective pressures may mean that plants
  cannot evolve to respond optimally to both pollinators and herbivores. Put another
  way, stronger selective pressure from herbivores might cause phenotypic changes
  that disrupt phylogenetic signal in pollinators, or vice versa. This could result from
  asymmetric degree distributions: within a single system, most plants tend to interact
  with many pollinators \emph{or} many herbivores but not both~\citep{Melian2009,Pockock2012,Astegiano2017}.
  These asymmetric interactions may also affect higher-order network structures such as
  modularity or nestedness~\citep{Astegiano2017}. The nature of the effects of multiple interaction types on both phylogenetic signal in interactions and overall network structure is, however, still an open question deserving of much more research.

@@

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[height=.75\textwidth]{Figures/dataplots/observed_vs_random.eps}}
    \end{center}
     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance (representing the change in log odds of a pair of plants sharing an interaction partner) was signficantly different from 0 for each network. Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks. Thick, dashed lines represent the mean slopes across all networks of each type. The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines. For both network types, the slopes obtained from permuted networks were always very close to 0. }
    \label{obs_vs_random} 
  \end{figure}
